|

### 2021-12-16 06-Chp-IPD-Analysis.Rmd
Range of updates

&nbsp;<!----------------------------------------------------------------------->  
(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data

@@

<!----------------------------------------------------------------------------->
(ref:covariateSummary-caption) Summary of characteristics for cohorts included in the IPD  analysis

@@

The results from the main effect analysis across the varying lipid fractions on each dementia outcome considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively. There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`). For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd-cap))

@@

<!----------------------------------------------------------------------------->
(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses for the all-cause dementia outcome.

@@

<!----------------------------------------------------------------------------->
(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.

>>>>

&nbsp;<!----------------------------------------------------------------------->  
(ref:dataExcluded-caption) __Exclusion reasons for cohorts providing data__ - Number of cohorts approach and the reasons for a lack of data access, stratified by whether the cohort was identified by the systematic review or via the DPUK.

@@

<!----------------------------------------------------------------------------->
(ref:covariateSummary-caption) __Characteristics of IPD cohorts__ - Summary of characteristics for cohorts included in the IPD analysis. Variables not available from a cohort are denoted by "-". See Appendix \@ref(appendix-ipd-covariate-matrix) for details on the level of missing data within collected variables.

@@

The results from the main effect analysis across the varying lipid fractions on each dementia outcome considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively. There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`). For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd))

@@

<!----------------------------------------------------------------------------->
(ref:ipdModelComparison-cap) __Comparison of partially- and maximally-adjusted model__ - Results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses for the all-cause dementia outcome were compared for the two cohorts containing a full set of covariates (EPIC, Whitehall II).

@@

<!----------------------------------------------------------------------------->
(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ - Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.

### 2021-12-16 07-Chp-Triangulation.Rmd
Range of updates

\blandscape
<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) Summary of studies included in this thesis and used as evidence sources in this triangulation exercise. Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.

@@

(ref:priorsAdd-caption) __Prior distributions mapped to different extents of bias.__ Prior values assigned to additive and proportional biases, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$. For additive biases, two scenarios were defined (see main text). Note that proportional biases are defined on the log scale for ease of calculation, but are exponentiated prior to their use for adjustment.

@@

<!----------------------------------------------------------------------------->
(ref:priorsIndirect-caption) Prior distributions for extent of indirectness, on the log scale.

>>>>

\blandscape
<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) __Summary of research designs included in this thesis__ -The research projects performed as part of this thesis and used as evidence sources in this triangulation exercise are summarised. Note that Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.

@@

(ref:priorsAdd-caption) __Prior distributions mapped to different extents of bias__ - Prior values assigned to additive and proportional biases, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$. For additive biases, two scenarios were defined (see main text). Note that proportional biases are defined on the log scale for ease of calculation, but are exponentiated prior to their use for adjustment.

@@

<!----------------------------------------------------------------------------->
(ref:priorsIndirect-caption) __Prior distributions mapped to different extents of indirectness__ - Prior values assigned to proportional indirectness, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$. Note that all indirectness in this analysis was defined _a priori_ to be proportional, and so no distributions for additive indirectness were defined.

### 2021-12-16 08-Discussion.Rmd
Range of updates

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = TRUE}
Hold
```

(ref:discussion-quote) --- Hold

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = TRUE}
Science knows it doesn't know everything.

Otherwise, it'd stop.
```

(ref:discussion-quote) --- Dara Ó Briain, 2008[@obriain2008]
